Environmental stress affects niche breadth in plant-pollinator communities

### 2019-11-16 paper/manuscript.Rmd
Remove unnecessary code

```{r tab-model-comparison}
model_ranking$waic %>%
  purrr::map(~.$estimates["waic", ]) %>%
  purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
  dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
                formula = kableExtra::cell_spec(formula, format = "latex", 
                                                bold =nchar(formula) == max(nchar(formula)))) %>% 
   knitr::kable("latex", 
               booktabs = TRUE, 
               digits = c(0,0,0), 
               format.args = list(big.mark = ","), 
               col.names = c("predictors", "WAIC", "SE"),
               escape = FALSE,
               linesep = "",
               caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives. We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO). The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking. We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
  kableExtra::kable_styling(font_size = 8) #%>%
  # kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
# 
# waic_scores <- as.data.frame(model_ranking$waic) %>%
#   tibble::rownames_to_column(var = "formula") %>%
#   dplyr::select(formula, waic)
# 
# loo_scores <- as.data.frame(model_ranking$loo) %>%
#   tibble::rownames_to_column(var = "formula") %>%
#   dplyr::select(formula, elpd_diff, se_diff,  looic) 
# 
# loo_scores %>%
#   dplyr::inner_join(waic_scores, by = "formula") %>%
#   dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
#                 formula = kableExtra::cell_spec(formula, format = "latex", 
#                                                 bold =nchar(formula) == max(nchar(formula)))) %>%
#   knitr::kable("latex", 
#                booktabs = TRUE, 
#                digits = c(0,0,1,0,0), 
#                format.args = list(big.mark = ","), 
#                col.names = c("predictors", "$\\Delta$", "$SE_{\\Delta}$", "IC", "WAIC"),
#                escape = FALSE,
#                linesep = "",
#                caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives. We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO). The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking. We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
#   kableExtra::kable_styling(font_size = 8) %>%
#   kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
```

>>>>

```{r tab-model-comparison}
model_ranking$waic %>%
  purrr::map(~.$estimates["waic", ]) %>%
  purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
  dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
                formula = kableExtra::cell_spec(formula, format = "latex", 
                                                bold =nchar(formula) == max(nchar(formula)))) %>% 
   knitr::kable("latex", 
               booktabs = TRUE, 
               digits = c(0,0,0), 
               format.args = list(big.mark = ","), 
               col.names = c("predictors", "WAIC", "SE"),
               escape = FALSE,
               linesep = "",
               caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives. We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO). The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking. We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
  kableExtra::kable_styling(font_size = 8) #%>%
```
